IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-28 assets/waveform_subband.tex
:chart_with_upwards_trend: Update plots

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,3.503in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.5413547897652\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_I$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	1.17726395475229\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_P$}

@@

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,2.747in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.339248611366759\\
2	2.51030400792355\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.223894740731443\\
2	1.02080999862228\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.992in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0454113496416176\\
2	0.0749432241788367\\
3	0.174436784198804\\
4	1.28942850163426\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.596937403868726\\
2	0.757813025699412\\
3	0.93101405396448\\
4	1.34495281524672\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.237in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00380240006943849\\
2	0.00503538441019884\\
3	0.00673935788269168\\
4	0.00928493526066052\\
5	0.0137641701895959\\
6	0.0224279293816095\\
7	0.0491218000319466\\
8	0.236399650887243\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.57240069726828\\
2	0.707532355159161\\
3	0.813056816207979\\
4	0.908886023167598\\
5	0.981885468475696\\
6	1.04528299395164\\
7	1.09956151160637\\
8	1.1844120256085\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,0.481in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00113001858729917\\
2	0.00128319910359356\\
3	0.00145615657965543\\
4	0.00165374633344438\\
5	0.00187706123944821\\
6	0.00215590582737282\\
7	0.00249082687044019\\
8	0.00291806514852023\\
9	0.00347094235515533\\
10	0.00420624059995467\\
11	0.00519447041447467\\
12	0.00655192372378942\\
13	0.00843364500565299\\
14	0.0114362629486765\\
15	0.0171822844859615\\
16	0.0313917536030629\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.407704437098618\\
2	0.463687310263386\\
3	0.512310122105\\
4	0.556819078359945\\
5	0.597811034393655\\
6	0.633731204224058\\
7	0.66976207094552\\
8	0.70029218188591\\
9	0.730728208302655\\
10	0.756260014823004\\
11	0.78063608646419\\
12	0.800901192040989\\
13	0.818115628024539\\
14	0.831455258593228\\
15	0.841240065783435\\
16	0.848873422011028\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,3.503in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.82172700965795\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_I$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000289213065829642\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_P$}

@@

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,2.747in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.295470946033806\\
2	2.78041553969328\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	6.88515292983531e-06\\
2	7.11243494475005e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.992in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00886602819700381\\
2	0.0237787230194659\\
3	0.108070855596065\\
4	1.1713310546201\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.633626542983812\\
2	0.829836144183102\\
3	0.976226628588797\\
4	1.35354289111746\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.237in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00167790645812327\\
2	0.00228016548777977\\
3	0.00318742185439004\\
4	0.00462726511721075\\
5	0.00716743728878421\\
6	0.0129273763723776\\
7	0.0308460700090715\\
8	0.115533318647694\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.603245855871981\\
2	0.755456602981771\\
3	0.858512489463287\\
4	0.953124795407537\\
5	1.02704466315581\\
6	1.08592420449446\\
7	1.13090925633169\\
8	1.18526539633296\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,0.481in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000617491691008369\\
2	0.000717776254822589\\
3	0.000835285279992789\\
4	0.000979591082427033\\
5	0.00115487030006212\\
6	0.00136293515999463\\
7	0.00161619354701616\\
8	0.00191279748068678\\
9	0.00227218304658774\\
10	0.0026908090305821\\
11	0.00319938829308565\\
12	0.00381122202979217\\
13	0.00474535479665619\\
14	0.00756353464992525\\
15	0.017474797658002\\
16	0.0547436973724798\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.418853266349202\\
2	0.478839773751748\\
3	0.529812149718329\\
4	0.573539152412764\\
5	0.611663102441733\\
6	0.642886720358442\\
7	0.677359347479036\\
8	0.701877932539796\\
9	0.729554340449397\\
10	0.748421821359951\\
11	0.768367609874633\\
12	0.782658242865203\\
13	0.796571330906253\\
14	0.806933582871612\\
15	0.818312174451126\\
16	0.833414484583038\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
